\documentclass[margin,line]{res}

\usepackage{hyperref}
\hypersetup{colorlinks=True, urlcolor=cyan}

\usepackage{multicol}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{$\enumerate$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{-0.3in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\newenvironment{list3}{
  \begin{list}{$\description$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0in}}}{\end{list}}

\begin{document}

\name{Justin Howard Bolden Barnowski \vspace*{1.35cm}}

\begin{resume}

\section{\sc Contact Information}
\begin{tabular}{@{}p{3in}p{4in}}
{\bf Phone:  } (312) 690 - 9828\\
{\bf E-mail: } {\tt jbarno54@gmail.com} \\
{\bf Website:} \url{https://github.com/jbarno} \\
\end{tabular}


\section{\sc Education}
  {\bf University of Michigan}, Ann Arbor, MI \hfill {\bf Aug `10 - Dec `13}\\
  {\em B.S.E. Computer Science, Cum Laude}


\section{\sc Employment}

\begin{list1}


\item [] {\bf Zipline International, LLC}, San Francisco, CA\\
\item [] {\em Site Reliability Engineer} \hfill {\bf April `22 - Feb `23}

\begin{list2}
\item  Designed internal authorization and authentication systems.
\item  Developed global visualizations of life saving drone delivery system.
\item  Led hardware level administration of new delivery sites around the world.
\item  Maintained CI/CD systems.
\item  Maintained 24/7 On-Call rotations.
\item  Database administration for end-user action tracking.
\item  Integrated network redundancy for lower-risk monitoring. \\
\end{list2}


\item [] {\bf Neighborhoods.com, LLC}, Chicago, IL\\
\item [] {\em DevOps and Enterprise Services Manager} \hfill {\bf Oct `21 - March `22}

\begin{list2}
\item  Remediated newly uncovered vulnerabities in underlying open source software.
\item  Led war room sessions through numerous AWS outages.
\item  Developed reusuable infrastructure as code for deploying Postgres clusters on AWS RDS.
\item  Led and completed the hiring process for multiple technical positions.
\item  Maintained internal authorization and authentication systems.
\item  Assisted in onboarding and offboarding of employees as needed.\\
\end{list2}

\item [] {\em DevOps Engineer} \hfill {\bf Oct `20 - Oct `21 }

\begin{list2}
\item  Deployed DataDog to Kubernetes clusters for enhanced service tracing and Real User Monitoring.
\item  Configured PagerDuty alerts to alert teammates of issues, including silencing/queuing of
non-critical alerts during off-hours.
\item  Configured Pod Security Policies to secure contanerized environments.
\item  Deployed Machine Learning models to benefit the business's bottom line.
\item  Utilized Packer and Ansible to update nodes running Kubernetes control plane components.
\item  Wrote a minimal Golang based network monitoring daemon to detect and mitigate known
Linux kernel bugs.
\item  Extended existing Helm charts to ease containerized deployments.
\item  Developed an organizational strategy for utilizing Github Actions.
\item  Updated and secured legacy CI systems running on Jenkins.\\
\end{list2}

\item [] {\bf DocuSign}, Chicago, IL\\
\item [] {\em Linux DevOps Engineer} \hfill {\bf April `19 - Oct `20}

\begin{list2}
\item  Automated patching of Linux systems across multiple data centers.
\item  Augmented existing tools for the benefit of operators and developers.
\item  Uncovered and rectified numerous logic, configuration, and data flaws.
\item  Handled patching both physical and virtual infrastructure, containing data systems.
\item  Participated in FedRAMP audit interviews for renewal of SpringCM’s status.
\item  Tools utilized: SaltStack, Gitlab, VMWare, Hashicorp’s Consul and Vault.\\
\end{list2}

\item [] {\bf University of Chicago, Center for Data Intensive Science}, Chicago, IL\\
\item [] {\em Lead QA Engineer Genomic Data Commons} \hfill {\bf June `18 - March `19}

\begin{enumerate}
\item Led operational readiness review meetings (a Go No-Go, decision meeting) with multiple stakeholders
per release. The most common stakeholders were the Ontario Institue of Cancer Research
(OICR) and National Institue of Health (NIH). Found and presented existing system and data
defects to advise stakeholders on the best course of action.
\item Led a team of two FTE SDETs and four student interns validating and automating validation of
new features and regressions. Took on mentor status with a few students, advising them on how
to best achieve their goals. Interviewed numerous DevOps and SDET candidates. Reviewed tens of
thousands lines of code across multiple disciplines.
\item Assisted with design and architecture development. Including versioning of files at the Petabyte
scale, segmenting data between users, and quarterly meetings at NIH headquarters to discuss
future infastructure improvements and workflow designs.
\item Utilized the python library PyPOM (Page Object Model) to greatly reduce copy and pasted test
code, and increase the maintainablity of the testing infastructure. This library was instrumental in
giving all testers a consistent way to solve timing problems in test code.
\end{enumerate}
\item [] {\em Software Engineer in Test Genomic Data Commons} \hfill {\bf June `17 - June `18}

\begin{enumerate}
\item Made auto\_qa repository into a functional service. Auto\_qa was deployed as service within
a cluster to validate that particular cluster. We are able to run chrome headlessly both locally and on
an auto\_qa service. Additionally, these tests were able to be scheduled at regular intervals. Previously this was
a manual process to run auto\_qa locally while connected to a VPN to validate a given environment. Gained
the ability to conditionally execute tests which require authorization tokens. Finally, I developed over 150 tests
for auto\_qa for a total of 239 tests.
\item Worked within the gdcapi for both “unit” and end to end tests. Refactored the gdcapi unit tests to to
maintain consistent code coverage with reduced execution time (on TravisCI from 30 min to 8 min).
Allowed developers to move faster with the confidence that their changes did not have unintended consequences.
Automated (12/20) of the API regression tests by translating curl calls to simple
python tests utilizing the requests library. These tests ran daily, and freed up one manual tester for
half a day per release cycle. Identified pain points within the gdcapi around BAM slicing requests
producing unnecessary crosstalk through consul to other gdcapi machines.\\
\end{enumerate}

\item [] {\bf Tophatter Inc}, Palo Alto, CA\\
\item [] {\em Developer} \hfill {\bf June `16 - Feb `18}

\begin{list2}
\item  Upgraded Android application’s user interface to Google’s Material Design specifications.
\item  Orchestrated A/B tests to determine optimal user experience and fulfillment of Tophatter’s objectives.
\item  Learned Ruby to fix server-side bugs while also developing new features on the Android client.
\item  Extended the Android application internationally, specifically enabling multi-currency bidding.
\item  Libraries/Tools used while at Tophatter: databinding, crashlytics, eventBus, picasso, PubNub, FB and Google signup, and braintree payments.\\
\end{list2}

\item [] {\bf Ericsson Inc}, Santa Clara, CA\\
\item [] {\em Developer} \hfill {\bf June `15 - June `16}

\begin{list2}
\item Maintained and enhanced the web app portion of a multi-platform video streaming application (Similar to AT\&T U-Verse or Comcast Xfinity).
\item Augmented landing service, and multi-operator customization framework. Including enabling configurable Content-Security-Policy headers to better secure end users’ browser sessions.
\end{list2}

\item [] {\em Tester} \hfill {\bf March `14 - June `15}

\begin{list2}
\item Implemented automated tests using a selenium web driver in both C\# and javascript.
\item Scrum Master for multiple teams.\\
\end{list2}

\item [] {\bf Microsoft Inc}, Mountain View, CA\\
\item [] {\em SDET Intern} \hfill {\bf May `13 - July `13}

\begin{list2}
\item During a twelve week internship collaborated with the Test Tools and Infrastructure team to revamp failing test case triage process. Worked extensively with Team Foundation Server APIs.\\
\end{list2}

\item [] {\bf Garmin Inc}, Novi, MI\\
\item [] {\em SDET Intern} \hfill {\bf April `12 - Aug `12}

\begin{list2}
\item Modernized the semi-truck instrument cluster, radio, and navigation tools. Worked extensively with the J1939 CAN networks of the vehicle. Including mimicking a CAN network using EEPod’s MyCanic.
\end{list2}

\end{list1}

% \section{\sc Honors and Awards}
% \begin{tabular}{@{}p{3in}p{4in}}
% Branstrom Award Top 5 GPA of Freshmen              & {\bf March 11}\\
% Graduated Cum Laude GPA   3.329                    & {\bf Dec 13}\\
% HKN (Eta Kappa Nu)                                 & {\bf Fall 11}\\
% \end{tabular}

\section{\sc Professional Experience}

\begin{list1}
\item [] {\bf Black Hat}, Las Vegas, NV\\
\item [] {\em Student/Participant } \hfill {\bf Aug `14-`15}\\
\begin{list2}
\item Android Application Hacking
\item Uses and Misuses of Cryptography
\item Advanced Wi-Fi Penetration Testing
\item 0x7DF Mobile Application Bootcamp

\end{list2}
\end{list1}


\section{\sc Virtual}
\begin{list1}
\item [] {\bf Android Developement}
\begin{description}
\item Tophatter \hfill {\bf Android Java}
\item Ericsson \hfill {\bf Multi-Client Shell Interface}
\item Trend Phrase \hfill {\bf  UI Class}
\item Stock Stalkers \hfill {\bf Mobile U.I. Senior Project}
\item Friend Finder Yahoo’s Hack-U competition \hfill {\bf Fall `10}
\end{description}
\end{list1}
%Currently developing a text based Android game.


\section{\sc Real}

\begin{list1}
\item [] Running
\begin{description}
  \item Chicago Half Marathon\hfill {\bf  Sep 24th, `17 in 2:29:17 }
  \item Chicago Marathon,{\em  The Team to End AIDS} \hfill {\bf  Oct 9th, `11 in 5:35:42}
% Raised ~\$1,700 for Chicago Aids Foundation. Completed my first
% marathon after eight months of self-directed training.
\end{description}
\end{list1}

\section{\sc Buzz Words}
\begin{multicols}{3}
Languages
\begin{list2}
\item Bash
\item C++
\item Python
\item YAML
\item HCL
\item Java
\item Golang
\item PHP
\item PowerShell
\item Typescript
\item Web Developement
\item R
\item Erlang
\item Kotlin
\item C\#
\item Ruby
\end{list2}
\columnbreak
Tools+Envs
\begin{list2}
\item Terraform
\item Ansible
\item Packer
\item Consul
\item Vault
\item Systemd
\item LDAP
\item Keycloak
\item Docker
\item Kubernetes
\item Helm
\item Tilt
\item Earthly
\item DataDog
\item Elasticsearch
\item Postgres
\item nginx
\item PagerDuty
\item AWS
\item OpenStack
\end{list2}
\columnbreak
People Skills
\begin{list2}
\item Agile Development
\item Scrum Master
\item Manager
\item Administrator
\end{list2}
\end{multicols}

\end{resume}
\end{document}
